---
title: "Lab 6"
author: "Deanna Elliott"
date: "11/2/2021"
output: html_document
---

```{r setup, include=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Rank-Based Test Example ##

Mann-Whitney U (non-parametric alternative to an unpaired 2-sample t-test).

H0: Equal ranks (or medians)
HA: Ranks (or medians) are NOT equal

### Create Samples ###

'set.seed()' to create "pseudo-random, but reproducible samples"

```{r}

set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

Take a quick look at the distributions using 'hist()'

```{r}

hist(gp_1)
hist(gp_2)
```

Try a t-test so we can compare the results:

```{r}

ttest <- t.test(gp_1, gp_2)

#If these data were paired, I can just add the argument 'paired = TRUE' within the t.test() function
```

This p-value means that IF our samples are drawn from populations with the same mean (i.e. if the null hypothesis is true), there is `r round(ttest$p.value, 2)` probability of finding sample means *at least as different* as mine by random chance.

[A more comprehensive explanation of difference between groups... actual means, data spread, effect size]... there is no significant difference (t(df) = t-stat value, p = #).

### Mann-Whitney U Rank-Based Test

We use the 'wilcox.test' function to perform a two-sample t-test

```{r}

mwu <- wilcox.test(gp_1, gp_2)
```

This p-value means that if our samples are drawn from populations with the same median, there is a 28% chance of finding sample medians at least as different as mine by random chance.

No significant difference in medians (Mann-Whitney U; U = `r mwu$statistic`, p = `r round(mwu$p.value, 2)`).

The medians of group A (M = 22.4 g) and group B (M = )