---
title: "Lab 6"
author: "Deanna Elliott"
date: "11/2/2021"
output: html_document
---

```{r setup, include=TRUE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)

library(tidyverse)
library(palmerpenguins)
library(broom)
library(equatiomatic)
```

## Rank-Based Test Example ##

Mann-Whitney U (non-parametric alternative to an unpaired 2-sample t-test).

H0: Equal ranks (or medians)

HA: Ranks (or medians) are NOT equal

#### Create Samples

'set.seed()' to create "pseudo-random, but reproducible samples"

```{r}

set.seed(1414)
gp_1 <- sample.int(20, size = 15, replace = TRUE)

set.seed(1424)
gp_2 <- sample.int(30, size = 15, replace = TRUE)
```

Take a quick look at the distributions using 'hist()'

```{r}

hist(gp_1)
hist(gp_2)
```

Try a t-test so we can compare the results:

```{r}

t_test <- t.test(gp_1, gp_2)

#If these data were paired, I can just add the argument 'paired = TRUE' within the t.test() function
```

This p-value means that IF our samples are drawn from populations with the same mean (i.e. if the null hypothesis is true), there is `r round(t_test$p.value, 2)` probability of finding sample means *at least as different* as mine by random chance.

[A more comprehensive explanation of difference between groups... actual means, data spread, effect size]... there is no significant difference (t(df) = t-stat value, p = #).

#### Mann-Whitney U Rank-Based Test

We use the 'wilcox.test' function to perform a two-sample t-test

```{r}

mwu <- wilcox.test(gp_1, gp_2)
```

This p-value means that if our samples are drawn from populations with the same median, there is a 28% chance of finding sample medians at least as different as mine by random chance.

No significant difference in medians (Mann-Whitney U; U = `r mwu$statistic`, p = `r round(mwu$p.value, 2)`).

The medians of group A (M = 22.4 g) and group B (M = 31.2 g) did not differ significantly (Mann-Whitney U; ...).

## Simple Linear Regression 

Two *continuous quantitative* variables that you are trying to understand the relationship between, and you think that a linear relationship makes sense.

Use the 'penguins' data from {palmerpenguins}, exploring flipper length (x) vs body mass (g).

```{r}

#Use view(penguins) to look at data
# Make an exploratory scatterplot of flipper length vs body mass

ggplot(data = penguins,
      aes(x = flipper_length_mm, y = body_mass_g)) +
  geom_point() +
  geom_smooth(method = "lm")
```

#### Find the Model Estimates (Coefficients)

Use the 'lm()' function for linear model.

```{r}

penguin_lm <- lm(body_mass_g ~ flipper_length_mm, data = penguins)
```

Model Coefficients: `r penguin_lm$coefficients`
Flipper Length Coefficient: `r penguin_lm$coefficients[2]`

#### Use 'broom::tidy()' to get stats on the linear regression

```{r}

penguin_lm_tidy <- tidy(penguin_lm)
```

#### Use 'broom::glance()' to get output of model fit and statistical significance

```{r}

penguin_lm_glance <- glance(penguin_lm)
```

#### Use equatiomatic::extract_eq() to return model in LaTex

```{r}

extract_eq(model = penguin_lm, use_coefs = TRUE)
```

#### Use plot() function to automatically produce diagnostic plots

```{r}

plot(penguin_lm)
```



$\frac{apples}{bananas}$
